Transient dynamics of granular piles: continuum v discrete modelling

### 2016-07-14 paper.tex
Removed CD results from runout and time plots

The flow involves a transient phase with a change in the geometry of the pile 
followed by continuous spreading. The gradient of input energy applied to the 
granular slope mimics a horizontal quake. Despite the creation 
of a cavity behind the flowing mass, the granular heap remains in 
contact with the left wall irrespective of the input 
energy.~\Cref{fig:Runout_Eo_MPM_CD_DEM} shows the normalised run-out distance 
$(L_f - L_0)/L_0$ and total run-out time $t_f$ as a function of the input 
energy $E_0$. Two regimes characterised by a power-law relation between 
the run-out distance and time as a function of $E_0$ can be observed. In the 
first regime, corresponding to the range of low input energies $E_0 < 40 \ 
mgd$, the run-out distance observed varies as $L_f \propto (E_0)^\alpha$ with 
$\alpha 
\simeq 0.206 \pm 0.012$ over nearly one decade. Overall, the run-out distance 
predicted by the continuum approach matches the DEM simulations. At very low 
energies, DEM simulations show longer run-out distance due to local 
fluidisation. The difference in the run-out between DEM and CD arise mainly 
from the scales of description and the inelastic nature of Contact Dynamics. 
Similar behaviour between DEM and CD approaches was observed 
by~\citet{Radjai1997}.

@@

\begin{figure}[tbph]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/Runout_Eo_MPM_CD_DEM}
    \caption{Run-out distance as a function of normalised input kinetic energy.}
    \label{fig:Runout_Eo_MPM_CD_DEM}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/Tf_vs_Eo_Slope}
    \caption{Duration of run-out as a function of normalised input kinetic energy.}
    \label{fig:Tf_vs_Eo_Slope}
  \end{subfigure}
  \caption{Evolution of run-out and time as a function of the normalised input 
  energy for a pile subjected a gradient horizontal energy.}
  \label{fig:Slope}
\end{figure}

>>>>

The flow involves a transient phase with a change in the geometry of the pile 
followed by continuous spreading. The gradient of input energy applied to the 
granular slope mimics a horizontal quake. Despite the creation 
of a cavity behind the flowing mass, the granular heap remains in 
contact with the left wall irrespective of the input 
energy.~\Cref{fig:runout_eo_mpm_dem} shows the normalised run-out distance 
$(L_f - L_0)/L_0$ and total run-out time $t_f$ as a function of the input 
energy $E_0$. Two regimes characterised by a power-law relation between 
the run-out distance and time as a function of $E_0$ can be observed. In the 
first regime, corresponding to the range of low input energies $E_0 < 40 \ 
mgd$, the run-out distance observed varies as $L_f \propto (E_0)^\alpha$ with 
$\alpha 
\simeq 0.206 \pm 0.012$ over nearly one decade. Overall, the run-out distance 
predicted by the continuum approach matches the DEM simulations. At very low 
energies, DEM simulations show longer run-out distance due to local 
fluidisation. The difference in the run-out between DEM and CD arise mainly 
from the scales of description and the inelastic nature of Contact Dynamics. 
Similar behaviour between DEM and CD approaches was observed 
by~\citet{Radjai1997}.

@@

\begin{figure}[tbph]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/runout_eo_mpm_dem}
    \caption{Run-out distance as a function of normalised input kinetic energy.}
    \label{fig:runout_eo_mpm_dem}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figs/Tf_vs_Eo_Slope}
    \caption{Duration of run-out as a function of normalised input kinetic energy.}
    \label{fig:Tf_vs_Eo_Slope}
  \end{subfigure}
  \caption{Evolution of run-out and time as a function of the normalised input 
  energy for a pile subjected a gradient horizontal energy.}
  \label{fig:Slope}
\end{figure}
